Baseline centering problem

### 2018-12-11 paper/tangotd.tex

This equation is wildly underdetermined. For instance, if $V$ is a
solution then $-V$ is also a solution...

>>>>

This equation is wildly underdetermined. For instance, if $V$ is a
solution then $-V$ is also a solution.

More generally, in dim $>1$, an equation such as $\abs{\partial
V(s)/\partial s}=-R(s)$ leaves total freedom as to the direction of the
gradient of $V$. Thus, with a randomly initialized $V$, my guess is that
early TD-like optimization would ``freeze'' upon random choices of local
directions of the gradient of $V$, each corresponding to a local belief
that ``the optimum lies in this direction''. Regions with different
directions of $\partial
V(s)/\partial s$ would meet on a $(D-1)$-dimensional set where Bellman
would be violated, but Bellman would still be satisfied on a set of
measure $1$.

Thus, off-policy algorithms based on sampling random transitions $(s,s')$
from a dataset would be slow to detect a problem, while on-policy (or
partly on-policy) algorithms would ``follow the local belief'' until
reaching a state where it becomes clear that this belief is unfounded, or
until they reach infinity.
